---
title: "Automated discrimination"
# author: "Moritz Zajonz"
# date: "9/10/2020"
output:
  html_document: 
    toc: yes
    df_print: kable
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8
)
```

```{r echo=FALSE,eval=TRUE}
options(scipen = 42)
source("05_data_pipeline.R")
```

# Variable explanation

The ad reports from Google and Facebook were cleaned and restructured to the same set of variables:

- *country*: the country the ad was targeted for
- *job*: the type of employment ad that was shown
- *gender*: assumed gender of the audience; impressions with unknown gender are filtered out in this report and calculations are based on data points with known gender
- *clicks*: number of clicks on ad — cumulative
- *impressions*: number of times ad was shown — cumulative
- *ctr*: click-through-rate; share of clicks per impression
- *datetime*: date and time of data points; this is based on time of manual downloads of reports every few minutes (at more or less regular intervals)
- *time*: hours passed since first impressions were registered
- *impr_rel*: share of all impressions of an ad at that time

**Note**: For the data for each of the following figures, see the folder “data/output/”, where you'll also find the full, clean dataset for each country.

# Point 1: Discrimination with no audience targeting

## By Google Ads

```{r}
google_overall_share <- google_male_female %>%
  group_by(country) %>% 
  slice_max(datetime) %>% 
  ungroup() %>%
  group_by(job, gender) %>% 
  summarise(impressions = sum(impressions)) %>% 
  ungroup() %>% 
  group_by(job) %>% 
  mutate(impr_rel = impressions/sum(impressions)) %>% 
  ungroup() %>%
  pivot_wider(names_from = gender, values_from = impressions:impr_rel) #%>%
# TODO: margin of error
  # group_by(job) %>%
  # mutate(moe_fem = sd(impr_rel_female)/sqrt(length(impr_rel_female))*qnorm(.975)) %>% View
  # mutate(lower = binom.test(c(impressions_female, impressions_male))[["conf.int"]][1],
  #        upper = binom.test(c(impressions_female, impressions_male))[["conf.int"]][2])

# Plot
google_overall_share %>% 
  select(job,
         # lower, 
         # upper,
         impressions = impressions_female, 
         impr_rel = impr_rel_female) %>% 
  ggplot(aes(y = job %>% fct_reorder(., impr_rel)))+
  # geom_errorbarh(aes(xmin = lower, xmax = upper), height = .2)+
  geom_point(aes(x = impr_rel), color = "#7fc97f")+
  scale_x_continuous(limits = c(0,1), labels = scales::percent)+
  labs(title = "Overall",
       x = paste0("Female share of impressions\nfor employment ad on Google"),
       y = "Employment ad",
       caption = "Figure 1")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```

### Corresponding data

```{r}
google_overall_share %>% 
  select(job,
         # lower, 
         # upper,
         impressions = impressions_female, 
         impr_rel = impr_rel_female) %T>% 
  write.csv(file = "output/data/figure_1.csv", row.names = FALSE) %>%  
  arrange(-impr_rel)
```

```{r fig.width=10, fig.height=7}
# Plot
google_male_female %>%
  filter(gender == "female") %>%
  group_by(country) %>% 
  slice_max(datetime) %>%
  ungroup() %>% 
  mutate(job = reorder_within(job, impr_rel, country)) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job), color = "#7fc97f")+
  scale_y_reordered()+
  scale_x_continuous(limits = c(0,1), labels = scales::percent)+
  labs("Per Country",
       x = paste0("Female share of impressions\nfor employment ad on Google"),
       y = "Employment ad",
       caption = "Figure 2")+
  facet_wrap(~country, scales = "free_y")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```

### Corresponding data

```{r}
google_male_female %>%
  filter(gender == "female") %>%
  group_by(country) %>% 
  slice_max(datetime) %>%
  ungroup() %>% 
  select(country, job, gender, impr_rel)%T>%
  write.csv(file = "output/data/figure_2.csv", row.names = FALSE) %>%  
  arrange(country, -impr_rel)
```


## By Facebook Ads

```{r}
facebook_overall_share <- facebook_male_female %>%
  group_by(country) %>% 
  slice_max(datetime) %>% 
  ungroup() %>%
  group_by(job, gender) %>% 
  summarise(impressions = sum(impressions)) %>% 
  ungroup() %>% 
  group_by(job) %>% 
  mutate(impr_rel = impressions/sum(impressions)) %>% 
  ungroup()

# Plot
facebook_overall_share %>% 
  filter(gender == "female") %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  scale_x_continuous(limits = c(0,1), labels = scales::percent)+
  labs(x = paste0("Female share of impressions\nfor employment ad on Facebook"),
       y = "Employment ad",
       caption = "Figure 3")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```

### Corresponding data

```{r}
facebook_overall_share %>% 
  filter(gender == "female") %>% 
  select(-impressions) %T>%
  write.csv(file = "output/data/figure_3.csv", row.names = FALSE) %>%  
  arrange(-impr_rel)
```

```{r fig.width=10, fig.height=7}
# Plot
facebook_male_female %>%
  filter(gender == "female") %>%
  group_by(country) %>% 
  slice_max(datetime) %>%
  ungroup() %>% 
  mutate(job = reorder_within(job, impr_rel, country)) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  scale_x_continuous(limits = c(0,1), labels = scales::percent)+
  scale_y_reordered()+
  labs(title = "Overall",
       x = paste0("Female share of impressions\nfor employment ad on Facebook"),
       y = "Employment ad",
       caption = "Figure 4")+
  facet_wrap(~country, scales = "free_y")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```

### Corresponding data

```{r}
facebook_male_female %>%
  filter(gender == "female") %>%
  group_by(country) %>% 
  slice_max(datetime) %>%
  ungroup() %>% 
  select(country, job, gender, impr_rel) %T>%
  write.csv(file = "output/data/figure_4.csv", row.names = FALSE) %>% 
  arrange(country, -impr_rel)
```

# Point 2: Click-through-rate doesn't influence impressions

## Google

```{r fig.width=10, fig.height=7}
google_male_female %>% 
  pivot_wider(names_from = gender, values_from = c(clicks, impressions, ctr, impr_rel)) %>%
  mutate(impr_rel_diff = impr_rel_female-impr_rel_male,
         ctr_diff = ctr_female - ctr_male) %>% 
  ggplot()+
  geom_point(aes(x = ctr_diff, y = impr_rel_diff), alpha = .4)+
  scale_x_continuous(labels = scales::percent)+
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Click-through-rate vs. Impressions on Google",
       subtitle = "Difference in percentage points between female and male audience\nDarker points indicate overlapping points",
       x = "Female audience clicks more often than male audience →",
       y = "← Male — audience sees ads more often — Female →",
       caption = "Figure 5")+
  facet_wrap(~country, scales = "free")+
  theme_minimal()

# Corresponding data
ggplot_build(last_plot())$plot$data %>%
  select(country, job, impr_rel_diff, ctr_diff) %>%
  write.csv(file = "output/data/figure_5.csv", row.names = FALSE)

# TODO: calculate actual correlation coefficients per country
# cor_test_fr <- google_male_female %>% 
#   filter(country == "FR") %>% 
#   pivot_wider(names_from = gender, values_from = c(clicks, impressions, ctr, impr_rel)) %>%
#   mutate(impr_rel_diff = impr_rel_female-impr_rel_male,
#          ctr_diff = ctr_female - ctr_male) %>% 
#   select_if(is.numeric) %>% 
#   replace_na(list(time = 0, 
#                   clicks_male = 0, 
#                   clicks_female = 0, 
#                   impressions_male = 0,
#                   impressions_female = 0,
#                   ctr_male=0,
#                   ctr_female=0,
#                   impr_rel_male=0,
#                   impr_rel_female=0,
#                   impr_rel_diff=0,
#                   ctr_diff=0))
#   
# 
# cor(cor_test)
```

**Note**: Data too large to display here. See "data/output/".

## Facebook

```{r fig.width=10, fig.height=7}
facebook_male_female %>% 
  pivot_wider(names_from = gender, values_from = c(clicks, impressions, ctr, impr_rel)) %>%
  mutate(impr_rel_diff = impr_rel_female-impr_rel_male,
         ctr_diff = ctr_female - ctr_male) %>% 
  ggplot()+
  geom_point(aes(x = ctr_diff, y = impr_rel_diff), alpha = .4)+
  scale_x_continuous(labels = scales::percent)+
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Click-through-rate vs. Impressions on Facebook",
       subtitle = "Difference in percentage points between female and male audience\nDarker points indicate overlapping points",
       x = "Female audience clicks more often than male audience →",
       y = "← Male — audience sees ads more often — Female →",
       caption = "Figure 6")+
    facet_wrap(~country, scales = "free")+
  theme_minimal()

ggplot_build(last_plot())$plot$data %>% 
  select(country, job, impr_rel_diff, ctr_diff) %>% 
  write.csv(file = "output/data/figure_6.csv", row.names = FALSE)
```

**Note**: Data too large to display here. See "data/output/".


# Point 3: Ad images influence ad delivery

## On Google

```{r}
# Plot
gg_truck2_male_female %>%
  filter(gender == "female") %>%
  slice_max(datetime) %>%
  ggplot()+
  geom_point(aes(x = impr_rel, y = variation %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  scale_x_continuous(limits = c(0,1), labels = scales::percent)+
  labs(x = paste0("Female share of impressions\nfor truck ad variations on Google in France"),
       y = "Employment ad",
       caption = "Figure 7")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```

### Corresponding data

```{r}
ggplot_build(last_plot())$plot$data %>%  
  select(country, job, variation, gender, impr_rel) %T>% 
  write.csv(file = "output/data/figure_7.csv", row.names = FALSE) %>% 
  arrange(-impr_rel)
```


## On Facebook

```{r}
# Plot
fb_truck2_male_female %>%
  filter(gender == "female") %>%
  slice_max(datetime) %>%
  ggplot()+
  geom_point(aes(x = impr_rel, y = variation %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  scale_x_continuous(limits = c(0,1), labels = scales::percent)+
  labs(x = paste0("Female share of impressions\nfor truck ad variations on Facebook in France"),
       y = "Employment ad",
       caption = "Figure 8")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```

### Corresponding data

```{r}
ggplot_build(last_plot())$plot$data %>%  
  select(country, job, variation, gender, impr_rel) %T>% 
  write.csv(file = "output/data/figure_8.csv", row.names = FALSE) %>% 
  arrange(-impr_rel)
```




```{r data_export}
countries <- c("CH", "DE", "ES", "FR", "PL")
for (c in countries) {
  google %>% 
    filter(country == c) %>% 
    write.csv(paste0("output/data/",c,"_google.csv"), row.names = FALSE)
  facebook %>% 
    filter(country == c) %>% 
    write.csv(paste0("output/data/",c,"_facebook.csv"), row.names = FALSE)
}
```

