---
title: "R Notebook"
output: 
  html_notebook: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r}
source("config.R")
source("01_data_import.R")
source("02_data_cleaning.R")
source("03_data_subsets.R")
```

# Running the pipeline

Style for the pipeline images

```{r fig.width=4, fig.height=2, dpi=300}
google_male_female %>%
    filter(gender == "female",
           country == "DE") %>%
  slice_max(datetime) %>% 
  ggplot()+
  # geom_vline(aes(xintercept = .5))+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  scale_x_continuous(limits = c(0,1))+
  # scale_y_discrete(expand = expansion(add = c(0.6,6))) +
  labs(x = paste0("Female share of impressions\nfor campaign in ", "DE on Google"),
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top",
        axis.title.y = element_blank())
```


Run this command to produce the images for all countries and both Facebook and Google:

```{r echo=TRUE,eval=FALSE}
source("05_data_pipeline.R")
```


# Germany

## Google

### Impressions

#### Total per gender

```{r}
google %>% 
  filter(country == "DE") %>% 
  slice_max(datetime) %>% 
  group_by(country, gender) %>% 
  summarise(impressions = sum(impressions)) %>%
  mutate(impressions_rel = (impressions/sum(impressions)) %>% round(4)) %>% 
  knitr::kable()
```


#### Shares for all genders

```{r}
google %>% 
  filter(country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job, color = gender))+
  geom_vline(aes(xintercept = .5))+
  scale_color_manual(values = c('#7fc97f','#beaed4','#fdc086'), name = "Gender")+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Share of impressions on Google",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```


#### Visualization of impression shares as point plot 

Similar to figure 8 of the original study

##### With gender type "undetermined"

```{r}
google %>% 
  filter(gender == "female",
         country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in DE on Google",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

##### Without gender type "undetermined"

```{r}
google_male_female %>% 
  filter(gender == "female",
         country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in DE on Google",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

#### Visualization of impression shares as bar chart


##### With gender type "undetermined"

```{r}
google %>% 
  filter(gender == "female",
         country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_col(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), fill = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in DE on Google",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

##### Without gender type "undetermined"

```{r}
google_male_female %>% 
  filter(gender == "female",
         country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_col(aes(x = impr_rel, 
               y = job %>% fct_reorder(., impr_rel)), 
           fill = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in DE on Google",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```


## Facebook

### Impressions 

#### Total per gender

```{r}
facebook %>% 
  filter(country == "DE") %>% 
  slice_max(datetime) %>% 
  group_by(gender) %>% 
  summarise(impressions = sum(impressions)) %>%
  mutate(impressions_rel = (impressions/sum(impressions)) %>% round(4)) %>% 
  knitr::kable()
```


#### Shares for all genders

```{r}
facebook %>% 
  filter(country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job, color = gender))+
  geom_vline(aes(xintercept = .5))+
  scale_color_manual(values = c('#7fc97f','#beaed4','#fdc086'), name = "Gender")+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Share of impressions on Facebook",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

#### Visualization as point plot 

Similar to figure 8 of the original study

##### Without gender type "undetermined"

Because the amount of "undetermined" impressions is negligible.

```{r}
facebook_male_female %>% 
  filter(country == "DE",
         gender == "female") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in DE on Facebook",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

#### Visualization as bar chart


##### Without gender type "undetermined"

```{r}
facebook_male_female %>% 
  filter(gender == "female",
         country == "DE") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_col(aes(x = impr_rel, 
               y = job %>% fct_reorder(., impr_rel)), 
           fill = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in DE on Facebook",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

### CTR and Impressions over time

```{r}
facebook %>% 
  filter(gender == "female",
         country == "DE") %>% 
  ggplot()+
  geom_line(aes(x = time, y = impr_rel, color = job))+
  geom_point(aes(x = time, y = impr_rel, color = job))+
  scale_color_discrete(name = "Employment ad")+
  labs(x = "Time in hours",
       y = "Female share of Impressions for Facebook in DE")+
  theme_minimal()+
  theme(legend.position = "top")
```





# France

## Facebook

### Impressions 

#### Total per gender

```{r}
facebook %>% 
  filter(country == "FR") %>% 
  slice_max(datetime) %>% 
  group_by(gender) %>% 
  summarise(impressions = sum(impressions)) %>%
  mutate(impressions_rel = (impressions/sum(impressions)) %>% round(4)) %>% 
  knitr::kable()
```


#### Shares for all genders

```{r}
facebook %>% 
  filter(country == "FR") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job, color = gender))+
  geom_vline(aes(xintercept = .5))+
  scale_color_manual(values = c('#7fc97f','#beaed4','#fdc086'), name = "Gender")+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Share of impressions on Facebook",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

#### Visualization as point plot 

Similar to figure 8 of the original study

##### Without gender type "undetermined"

Because the amount of "undetermined" impressions is negligible.

```{r}
facebook_male_female %>% 
  filter(gender == "female",
         country == "FR") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_point(aes(x = impr_rel, y = job %>% fct_reorder(., impr_rel)), color = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in FR on Facebook",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

#### Visualization as bar chart


##### Without gender type "undetermined"

```{r}
facebook_male_female %>% 
  filter(gender == "female",
         country == "FR") %>% 
  slice_max(datetime) %>% 
  ggplot()+
  geom_col(aes(x = impr_rel, 
               y = job %>% fct_reorder(., impr_rel)), 
           fill = "#7fc97f")+
  geom_vline(aes(xintercept = .5))+
  scale_x_continuous(limits = c(0,1))+
  labs(x = "Female share of impressions for campaign in FR on Facebook",
       y = "Employment ad")+
  theme_minimal()+
  theme(legend.position = "top")
```

### CTR and Impressions over time

```{r}
facebook %>% 
  filter(gender == "female",
         country == "FR") %>% 
  ggplot()+
  geom_line(aes(x = time, y = impr_rel, color = job))+
  geom_point(aes(x = time, y = impr_rel, color = job))+
  scale_color_discrete(name = "Employment ad")+
  labs(x = "Time in hours",
       y = "Female share of Impressions for Facebook in FR")+
  theme_minimal()+
  theme(legend.position = "top")
```




## Statistical test for significance

### Significance: Truck driver

The siginificance of the difference in impressions is big enough; the difference in clicks is not significant.

```{r}
x <- google_male_female %>%
  filter(gender == "female", job == "Truck driver",
         datetime == google_male_female %>% pull(datetime) %>% max()) %>%
  pull(impressions)
n <- google_male_female %>% 
  filter(job == "Truck driver",
         datetime == google_male_female %>% pull(datetime) %>% max()) %>%
  pull(impressions) %>% 
  sum()
binom.test(x,n)

x <- google_male_female %>%
  filter(gender == "female", job == "Truck driver",
         datetime == google_male_female %>% pull(datetime) %>% max()) %>%
  pull(clicks)
n <- google_male_female %>%
  filter(job == "Truck driver",
         datetime == google_male_female %>% pull(datetime) %>% max()) %>% 
  pull(clicks) %>%
  sum()
binom.test(x,n)
```




